---
title: "Aides Tests"
author: "Elisabet Mendoza"
date: "December 9, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(dplyr)
Scarolina<-read.csv(file="south_carolina_aides.csv",header=TRUE)
korea<-read.csv(file="korea_aides.csv",header=TRUE)
cenAfrica<-read.csv(file="central_africa_aides.csv",header=TRUE)
```

#Instructions

Three new preventative aides drugs were tested in clinical trials in 2015. The trial designs were modeled after the famous RV_144 Aides Trials in Tailand in 2009.  Analyze and report on the apparent effectiveness of the three different drugs. Does sex of the participant seem to be a factor for any of the drugs?

# Methods

In order to analyze and report on the apparent effectiveness of the three different drugs, I will run several tests. I will use bar charts to compare the information I will be filtering the information to be able to see if sex of the participant seem to be a factor for any of the drugs. I will analyze the garphical results and the numerical results. Then I will do chi-squared tests in order to be able to observe the P-value and interpret the null hypothesis.

# South Carolina

### Graphical Results

```{r}
barchartGC(~group + infected, data=Scarolina, type="percent", main = "South Carolina Male and Female")
```

Looking at the South Carolina barchart when we conbin male and female we can see that the populasion that recived the drug with about 5% and the populasion that recived the placebo with about 5% show littel to no difrence. The drug seams to have no efect against aids when we look at the male and female populasion together.

##### We will subset the data by sex to see if the drug is sex specific.

```{r}
ScarolinaM <- filter(Scarolina,sex=="M")
barchartGC(~group + infected, data=ScarolinaM, type="percent", main = "South Carolina Male")
```

Looking at the South Carolina barchart when we look at the male population only we can see that does whom recived the drug have about 7% infected with aids and those that recived the placebo only had about 5% infrcted with aids.

```{r}
ScarolinaF<-filter(Scarolina,sex=="F")
barchartGC(~group + infected, data=ScarolinaF, type="percent", main = "South Carolina Female")
```

Looking at the South Carolina barchart when we look at the female population only we can see that does whom recived the drug have about had about 4% of the pupolation infected with aids and those that recived the placebo had about 6% infected with aids.

### Numerical Results

```{r}
Scarolina_table <- xtabs(~group + infected, data = Scarolina)
rowPerc(Scarolina_table)
```

Here we can see that indeed there is olny a .14% difrence. This is an amount too small to consider significant.

```{r}
ScarolinaM_table <- xtabs(~group + infected, data = ScarolinaM)
rowPerc(ScarolinaM_table)
```

when we see the results for the male pupolation we can see that the drug may have had a revers effect. The diffrence from 5.27% of infected with the placebo and the incresed amount of 7.09% inthe population the recived the drug.

```{r}
ScarolinaF_table <- xtabs(~group + infected, data = ScarolinaF)
rowPerc(ScarolinaF_table)
```

### Inferential Results

```{r}
chisqtestGC(Scarolina_table)
```

```{r}
chisqtestGC(ScarolinaM_table)
```

```{r}
chisqtestGC(ScarolinaF_table)
```

# Central Africa

### Graphical Results
```{r}
barchartGC(~group + infected, data=cenAfrica, type="percent", main = "Central Africa Male and Female")
```

##### We will subset the data by sex to see if the drug is sex specific.

```{r}
cenAfricaM <- filter(cenAfrica,sex=="M")
barchartGC(~group + infected, data=cenAfricaM, type="percent", main = "Central Africa Male")
```

```{r}
cenAfricaF<-filter(cenAfrica,sex=="F")
barchartGC(~group + infected, data=cenAfricaF, type="percent", main = "Central Africa Female")
```

### Numerical Results

```{r}
cenAfrica_table <- xtabs(~group + infected, data = cenAfrica)
rowPerc(cenAfrica_table)
```

```{r}
cenAfricaM_table <- xtabs(~group + infected, data = cenAfricaM)
rowPerc(cenAfricaM_table)
```


```{r}
cenAfricaF_table <- xtabs(~group + infected, data = cenAfricaF)
rowPerc(cenAfricaF_table)
```

### Inferential Results

```{r}
chisqtestGC(cenAfrica_table)
```

```{r}
chisqtestGC(cenAfricaM_table)
```

```{r}
chisqtestGC(cenAfricaF_table)
```

# Korea

### Graphical Results
```{r}
barchartGC(~group + infected, data=korea, type="percent", main = "Central Africa Male and Female")
```

##### We will subset the data by sex to see if the drug is sex specific.

```{r}
koreaM <- filter(korea,sex=="M")
barchartGC(~group + infected, data=koreaM, type="percent", main = "Central Africa Male")
```

```{r}
koreaF<-filter(korea,sex=="F")
barchartGC(~group + infected, data=koreaF, type="percent", main = "Central Africa Female")
```

### Numerical Results

```{r}
korea_table <- xtabs(~group + infected, data = korea)
rowPerc(korea_table)
```

```{r}
koreaM_table <- xtabs(~group + infected, data = koreaM)
rowPerc(koreaM_table)
```


```{r}
koreaF_table <- xtabs(~group + infected, data = koreaF)
rowPerc(koreaF_table)
```

### Inferential Results

```{r}
chisqtestGC(korea_table)
```

```{r}
chisqtestGC(koreaM_table)
```

```{r}
chisqtestGC(koreaF_table)
```

# Conctusion